Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-10-08 paper.tex
fixed quantitative
addresses PR#27

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
Coherent spectroscopies are often described using the density matrix formalism in the interaction picture, where an n$^{\text{th}}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation:
\begin{equation}\label{LVNE}
	\dot{\rho}^{(n)} = \frac{1}{i \hbar} [H + V(t), \rho^{(n-1)}] + \dot{\rho}^{(n)}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
In systems where interactions with surroundings are relevant, expressions for $\dot{\rho}_R$ may be quite complicated due to intricate phenomena such as system-bath interactions and solvent-solute coupling, among others. \cite{Sung2001}
In the limit where input field pulse widths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write a time-independent relaxation matrix $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e., exponential relaxation, where $\Gamma$ is the system's dephasing rate. \cite{RN455, Sue1986, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
Thus, we write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$.
The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times. \cite{Raschke2002, Gaynor2017}

@@

\subsection{Vibronic Selection Rules}\label{Albrecht}
While the Placzek treatment provides the source of vibrationally HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to Albrecht's treatment of Raman spectroscopy (i.e., sum-over-states formalism).\cite{Albrecht1961, Ziegler1988} 
To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(\textbf{Q})) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter. \cite{BornOppenheimer, Tang1970}
We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.
It is worthwhile noting that the time-dependent Raman formalism developed by Heller \textit{et al.} can be applied to hyper-Raman scattering. \cite{Lee1979, Shoute2005, Silverstein2012}
However, since our goal is to expose the Quantum Mechanical aspects of HDFG spectroscopy, we choose to employ the typical sum-over-states formalism.

>>>>

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
Coherent spectroscopies are often described using the density matrix formalism in the interaction picture, where an n$^{\text{th}}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation:
\begin{equation}\label{LVNE}
	\dot{\rho}^{(n)} = \frac{1}{i \hbar} [H + V(t), \rho^{(n-1)}] + \dot{\rho}^{(n)}_R,
\end{equation}
where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
In systems where interactions with surroundings are relevant, expressions for $\dot{\rho}_R$ may be quite complicated due to intricate phenomena such as system-bath interactions and solvent-solute coupling, among others. \cite{Sung2001}
In the limit where input field pulse widths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write a time-independent relaxation matrix $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e., exponential relaxation, where $\Gamma$ is the system's dephasing rate. \cite{RN455, Sue1986, Sung2001}
While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, qualitative models to understand HDFG response.
Thus, we write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$.
The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times. \cite{Raschke2002, Gaynor2017}

@@

\subsection{Vibronic Selection Rules}\label{Albrecht}
While the Placzek treatment provides selection rules for vibrationally resonant HDFG output, it does not predict HDFG output as $\omega_2 + \omega_3$ is changed.
We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to Albrecht's treatment of Raman spectroscopy (i.e., sum-over-states formalism).\cite{Albrecht1961, Ziegler1988} 
To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(\textbf{Q})) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter. \cite{BornOppenheimer, Tang1970}
We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.
It is worthwhile noting that the time-dependent Raman formalism developed by Heller \textit{et al.} can be applied to hyper-Raman scattering. \cite{Lee1979, Shoute2005, Silverstein2012}
However, since our goal is to expose the Quantum Mechanical aspects of HDFG spectroscopy, we choose to employ the typical sum-over-states formalism.
